---
title: "Lab6"
author: "Yi Hung Chen, Kyriakos Papadopoulos"
date: "03/10/2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Description

This Package contains 3 different algorithms for solving the **knapsack problem**. The 3 algorithms that we use are

1.  Brute force search
2.  Dynamic Programming
3.  Greedy Heuristic

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

```{r setup}
library(Lab6)
```

### brute_force_knapsack(x,W,parallel = FALSE)

> The complexity of the algorithm is 2\^(n) as avaluates all possible combinations

-   x -\> The matrix which contains the weight and value of each item
-   W -\> The total weight that knapsack fit
-   parallel -\> By default is false and it gives the opportunity to the user to select if he/she wants to run the algorithm in parallel.

```{r, eval=TRUE, include=TRUE}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

The time that it takes to run the algorithm for n=16 is 144.68s

### knapsack_dynamic(x,W)

> This algorithm iterates all possible values of W. It will run in Wn.

-   x -\> The matrix which contains the weight and value of each item
-   W -\> The total weight that knapsack fit

```{r, eval=TRUE, include=TRUE}
knapsack_dynamic(x = knapsack_objects[1:800,], W = 3500)
```

The time that it takes to run the algorithm for n=500 is 2.28 seconds.

### greedy_knapsack(x,W)
> This algorithm will not give an exact result but it's complexity is nlogn

-   x -\> The matrix which contains the weight and value of each item
-   W -\> The total weight that knapsack fit

```{r, eval=TRUE, include=TRUE}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```

The time that it takes to run the algorithm for n=1000000 is 0.09s seconds.
